{Gravitational wave sources in our Galactic backyard:}\\{Predictions for BHBH, BHNS and NSNS binaries detectable with LISA

### 2022-01-22 paper/tex/sections/discussion.tex
nature may never be apparent, mass ratio not well measured

\subsection{Identification of GW sources}\label{sec:identify_sources}
It is important to note that, though we present predictions for the detection rates of specific DCO types, the nature of the source may not be immediately apparent from the gravitational wave signal. LISA can detect a variety of sources, from exoplanets \citep[e.g.][]{Tamanini+2019} to common-envelopes \citep[e.g.][]{Ginat+2020, Renzo+2021} that may cause confusion. However, by far the most prominent will be the population of Galactic WDWDs detectable with LISA, which will be several orders of magnitude larger than the population of the more massive DCOs that we focus on in this paper \citep[e.g.][]{Korol+2017}. It is therefore imperative that we consider how to distinguish NS and BH binaries from this much more numerous population of sources. In addition to distinguishing them from WDWDs, we must consider how to discriminate between BHBHs, BHNSs and NSNSs themselves.

@@

For separating the BHBH and BHNS population one could do so probabilistically given the properties that are measured, particularly the orbital frequency, mass ratio and eccentricity, since these distributions are fairly different for the two DCO types (see Fig.~\ref{fig:fiducial_pdf_distributions}). This method would pose a challenge, however, as it would likely only indicate which type was more likely rather than discriminate between them with strong evidence.

>>>>

\subsection{Identification of GW sources}\label{sec:identify_sources}
It is important to note that, though we present predictions for the detection rates of specific DCO types, the nature of the source may not be immediately \referee{(or ever)} apparent from the gravitational wave signal. LISA can detect a variety of sources, from exoplanets \citep[e.g.][]{Tamanini+2019} to common-envelopes \citep[e.g.][]{Ginat+2020, Renzo+2021} that may cause confusion. However, by far the most prominent will be the population of Galactic WDWDs detectable with LISA, which will be several orders of magnitude larger than the population of the more massive DCOs that we focus on in this paper \citep[e.g.][]{Korol+2017}. It is therefore imperative that we consider how to distinguish NS and BH binaries from this much more numerous population of sources. In addition to distinguishing them from WDWDs, we must consider how to discriminate between BHBHs, BHNSs and NSNSs themselves.

@@

For separating the BHBH and BHNS population one could do so probabilistically given the properties that are measured, particularly the orbital frequency and eccentricity, since these distributions are fairly different for the two DCO types (see Fig.~\ref{fig:fiducial_pdf_distributions}). This method would pose a challenge, however, as it would likely only indicate which type was more likely rather than discriminate between them with strong evidence.
